\chapter{Gran Pulse Cleanup}

Activate Mission 33 (next to green goblins on the right).
Warp to the Central Expanse ($\downarrow\downarrow\downarrow$).

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item \paradigmdeck{%
  				\paradigmline{Sazh}{Snow}{Vanille}}%
				{\paradigmline{\com}{(\com)}{\com}}%
				{\paradigmline{\com}{(\com)}{\sab}}%
				{\paradigmline{(\com)}{\sen}{(\med)}}%
				{\paradigmline{(\syn)}{(\rav)}{(\sab)}}%
				{\paradigmline{\syn}{\sen}{\med}}%
				{\paradigmline[4]{(\rav)}{\rav}{\sab}}%
			\item Battle Team
				\begin{itemize}
					\item Swap Sazh with Snow (1 $\leftrightarrow$ 2)
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\first}{[1] Cerberus (\com/\com/\com)}
\renewcommand{\second}{[2] Devastation (\com/\com/\sab)}
\renewcommand{\third}{[3] Solidarity (\com/\sen/\med)}
\renewcommand{\fourth}{[4] Guerilla (\syn/\rav/\sab)}
\renewcommand{\fifth}{[5] Protection (\syn/\sen/\med)}
\renewcommand{\sixth}{[6] Smart Bomb (\rav/\rav/\sab)}

Ride the chocobo to the mark (by the flying enemies' pass).

\begin{battle}{Mission 33: Adamanchelid}
	\begin{itemize}
		\item Same as in Chapter 12. Use [6] and [4] and yolo Wheelie
	\end{itemize}
\end{battle}

Grab the nearby chocobo (turn around and at the plateau where the Scarletite/M15 were) and activate Mission 57 (back green at the circle).
Warp to Yaschas Massif - Tsubaddran Highlands (mash A).

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item Battle Team
				\begin{itemize}
					\item Swap Snow with Sazh (1 $\leftrightarrow$ 2)
				\end{itemize}
		\end{itemize}
	\equip
		\begin{itemize}
			\item Snow
				\begin{itemize}
					\item Black Belt* $\rightarrow$ Aurora Scarf Lv.1
					\item General's Belt Lv.1 $\rightarrow$ Tetradic Tiara Lv.1
				\end{itemize}
			\item Vanille ($\rightarrow$)
				\begin{itemize}
					\item Sorcerer's Mark*
					\item Witch's Bracelet Lv.1
					\item Witch's Bracelet Lv.1
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

Run to the Vallis Media and engage the battle.

\begin{battle}{Mission 57: Sahagins \& Alraunes}
	\begin{itemize}
		\item \sixth
			\begin{itemize}
				\item Immediately shift
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Bravery-Enfire Sazh
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Blitz-Blitz
				\item Repeat until victory
			\end{itemize}
	\end{itemize}
\end{battle}

Run back and warp to the Base Camp ($\downarrow$).
Activate Mission 32 (up a bit) and warp to the Northern Highplain ($\downarrow\downarrow\downarrow$).
Mount the chocobo behind BK+M and run to the mission area by the lake.
Pre-empt the Amam.

\begin{battle}{Mission 32: Amam -- Pre-Empt}
	\begin{itemize}
		\item \sixth
			\begin{itemize}
				\item Flamestrike x1 ($\uparrow$) immediately
				\item Let Snow stagger, then shift
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Bravery-Enfrost Sazh
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Blitz
			\end{itemize}
	\end{itemize}
\end{battle}

Grab the chocobo and activate Mission 52 nearby (plateau where Geiseric was).

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item Default [5]
		\end{itemize}
	\end{itemize}
\end{menu}

Use a \textbf{Deceptisol} before the fight.

\begin{battle}{Mission 52: Zirnitra -- Pre-Empt}
	\begin{itemize}
		\item \fifth
			\begin{itemize}
				\item Auto-Support
				\item Bravery-Enfire Sazh
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Blitz-Attack-Blitz, \rav-buffer into [6]
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Cold Blood
			\end{itemize}
		\item \second
			\begin{itemize}
				\item Blitz-Blitz
				\item Repeat until victory, refreshing with [1]
			\end{itemize}
	\end{itemize}
\end{battle}

Activate Mission 59 at the circle (first purple from the left) and grab the nearest chocobo.
Warp to Sulyya Springs ($\uparrow\uparrow\uparrow\uparrow$).
Use a \textbf{Deceptisol} before the fight.

\begin{battle}{Mission 59: Zirnitra \& Frogs -- Pre-Empt}
	\begin{itemize}
		\item \fifth
			\begin{itemize}
				\item Quake
				\item Auto-Support
				\item Bravery-Enfire Sazh
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Blitz-Attack-Blitz, \rav-buffer into [6]
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Cold Blood
			\end{itemize}
		\item \second
			\begin{itemize}
				\item Attack x4
				\item Shift after Zirnitra has debuffs
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Repeat until Zirnitra dies
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Repeat until victory
			\end{itemize}
	\end{itemize}
\end{battle}

Activate Mission 63 (in front) and warp to the Northern Highplains ($\downarrow\downarrow\downarrow\downarrow$).
Take a chocobo to the mission and trigger the Cactuar cutscene on the way to keep your chocobo for after the mission.

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item \paradigmdeck{%
  				\paradigmline{Sazh}{Snow}{Vanille}}%
				{\paradigmline{\com}{\com}{\com}}%
				{\paradigmline{\com}{\com}{\sab}}%
				{\paradigmline{\com}{(\rav)}{(\sab)}}%
				{\paradigmline[4]{\syn}{\rav}{\sab}}%
				{\paradigmline{(\com)}{(\rav)}{(\rav)}}%
				{\paradigmline{\rav}{\rav}{\sab}}%
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\third}{[3] Ruthless (\com/\rav/\sab)}
\renewcommand{\fifth}{[5] Relentless Assault (\com/\rav/\rav)}

If you have $<3$ TP, use an \textbf{Ethersol}.

\begin{battle}{Mission 63: Adamantortoise}
	\begin{itemize}
		\item \fourth
			\begin{itemize}
				\item Summon
				\item Librascope
				\item Bravery-Haste Sazh
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Fire-Fira-Thunder-Fire
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Blitz-Blitz, \rav-buffer the first Blitz into [6]
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Repeat
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Repeat the first Blitz, \rav-buffer into [6] again
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Repeat
					\begin{itemize}
						\item Continue until $\sim$215\% chain
					\end{itemize}
			\end{itemize}
		\item \second
			\begin{itemize}
				\item Repeat until Bryn uses Arise
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Repeat Snow ($\downarrow$)
				\item Haste-Faith Vanille ($\uparrow$)
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Repeat until all debuffs have landed
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Repeat twice
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Repeat until victory, refreshing with [2]
			\end{itemize}
	\end{itemize}
\end{battle}

Get back on the chocobo behind you and activate Mission 16 (on the same platform).

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item Swap [3] and [4]
			\item \paradigmdeck{%
  				\paradigmline{Sazh}{Snow}{Vanille}}%
				{\paradigmline{\com}{\com}{\com}}%
				{\paradigmline{\com}{(\sen)}{(\med)}}%
				{\paradigmline{\syn}{\rav}{\sab}}%
				{\paradigmline{\com}{(\sen)}{(\med)}}%
				{\paradigmline[4]{(\syn)}{(\sen)}{(\med)}}%
				{\paradigmline{\rav}{\rav}{\sab}}%
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\second}{[2] Solidarity (\com/\sen/\med)}
\renewcommand{\third}{[3] Guerilla (\syn/\rav/\sab)}
\renewcommand{\fourth}{[4] Solidarity (\com/\sen/\med)}
\renewcommand{\fifth}{[5] Protection (\syn/\sen/\med)}

Run to the Font of Namva and enter the battle.

\begin{battle}{Mission 16: Sahagins \& Frogs}
	\begin{itemize}
		\item \fifth
			\begin{itemize}
				\item Auto-Support
				\item Bravery-Enfire Sazh
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Blitz-Blitz Ceratoraptors
				\item Repeat until victory, refresh with [2]/[4] when needed
			\end{itemize}
	\end{itemize}
\end{battle}

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item Battle Team
				\begin{itemize}
					\item Swap Sazh with Snow (1 $\leftrightarrow$ 2)
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

Get on the chocobo and activate Mission 54 (left of BK+M).
Run into the cutscene and retry the fight.
Use a \textbf{Fortisol} and engage the fight on the chocobo to keep it for after the fight.

\begin{battle}{Mission 54: Gigantuar}
	\begin{itemize}
		\item \fifth
			\begin{itemize}
				\item Summon
				\item Librascope
				\item Auto-Cover until Challenge lands
				\item X -- Gestalt
					\begin{itemize}
						\item Y -- Diamond Dust
					\end{itemize}
				\item Steelguard x5
				\item Wait for Enfire on Sazh
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Use Painkillers to get rid of Pain
				\item Use Steelguards to tank attacks
				\item Refresh Sazh and Vanille so that damage/healing can get done quickly
			\end{itemize}
	\end{itemize}
\end{battle}

Get on the chocobo and activate Mission 56 (circle, green stone).
Warp to Yaschas Massif - Tsubaddran Highlands (mash A).

\textbf{If 0 Deceptisols because only bought 17 before M55, do the next shop on the next save point and finish the menu for M62 afterwards.}

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item Battle Team
				\begin{itemize}
					\item Swap Snow with Sazh (1 $\leftrightarrow$ 2)
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

Run to the place from M4.
Use a \textbf{Deceptisol} before the fight.
Check Ethersol count for the next shop.

\begin{battle}{Mission 56: Ugallu \& Munchkins -- Pre-Empt}
	\begin{itemize}
		\item \fifth
			\begin{itemize}
				\item Bravery-Enfrost Sazh
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Blitz-Blitz until victory
			\end{itemize}
	\end{itemize}
\end{battle}

\begin{shop}{?}
	\begin{itemize}
		\item R\&D Depot
			\begin{itemize}
				\item Sell
					\begin{itemize}
						\item Accessories
							\begin{itemize}
								\item Growth Egg
							\end{itemize}
					\end{itemize}
				\item Buy
					\begin{itemize}
						\item Particle Accelerator up to x8
					\end{itemize}
			\end{itemize}
		\item Creature Comforts
			\begin{itemize}
				\item Buy
					\begin{itemize}
						\item Wicked Fang x41
						\item Sturdy Bone x72
						\item Barbed Tail x72
					\end{itemize}
			\end{itemize}
		\item B\&W Outfitters
			\begin{itemize}
				\item Buy
					\begin{itemize}
						\item Witch's Bracelet x3
						\item Sorcerer's Mark
					\end{itemize}
			\end{itemize}
		\item Eden Pharmaceuticals
			\begin{itemize}
				\item Buy
					\begin{itemize}
						\item Deceptisol x1
						\item Fortisol up to x3
						\item Aegisol up to x3
						\item Deceptisol until out (minimally up to x3)
					\end{itemize}
			\end{itemize}						
	\end{itemize}
\end{shop}

\begin{upgrade}
	\begin{itemize}
		\item Upgrade
			\begin{itemize}
				\item Accessories
					\begin{itemize}
						\item Witch's Bracelet x5
							\begin{itemize}
								\item Sturdy Bone/Barbed Tail/Wicked Fang
								\item Particle Accelerator x2/Bomb Core x17/Bomb Shell x44
							\end{itemize}
						\item \textit{If $<2$ Ethersols}, Energy Sash
							\begin{itemize}
								\item Bomb Core x3/Bomb Shell x7
								\item Dismantle it
							\end{itemize}
					\end{itemize}
			\end{itemize}
	\end{itemize}
\end{upgrade}
\vfill

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item \paradigmdeck{%
  				\paradigmline{Sazh}{Snow}{Vanille}}%
				{\paradigmline{\com}{(\rav)}{(\sab)}}%
				{\paradigmline{\com}{(\rav)}{\med}}%
				{\paradigmline{(\rav)}{(\sen)}{(\med)}}%
				{\paradigmline[4]{\com}{\sen}{\med}}%
				{\paradigmline{\syn}{\sen}{\med}}%
				{\paradigmline{\sen}{\sen}{\med}}%
		\end{itemize}
	\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Power Glove Lv.9 $\rightarrow$ Witch's Bracelet*
					\item Power Glove Lv.9 $\rightarrow$ Witch's Bracelet*
				\end{itemize}
			\item Snow ($\rightarrow$)
				\begin{itemize}
					\item Solaris
					\item Power Glove*
					\item Power Glove Lv.9
					\item Power Glove Lv.9
				\end{itemize}
			\item Vanille ($\rightarrow$)
				\begin{itemize}
					\item Sorcerer's Mark* $\rightarrow$ Witch's Bracelet*
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\first}{[1] Ruthless (\com/\rav/\sab)}
\renewcommand{\second}{[2] Diversity (\com/\rav/\med)}
\renewcommand{\third}{[3] Entourage (\rav/\sen/\med)}
\renewcommand{\sixth}{[6] Consolidation (\sen\sen\med)}

Warp to the Central Expanse ($\downarrow\downarrow$).
Activate Mission 62 (stone circle).
Use \textbf{Fortisol}, \textbf{Aegisol} and \textbf{Ethersol} before the fight.

\begin{battle}{Mission 62: Raktavija x2}
	\begin{itemize}
		\item \fourth
			\begin{itemize}
				\item Attack-Blitz, \rav-buffer into [3]
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Quake
				\item Cold Blood and shift
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Shift once Cold Blood is over
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Repeat on the other Raktavija, \rav-buffer into [3]
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Quake
				\item Repeat and shift
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Shift once Cold Blood is over
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Repeat on both with \rav-buffer until one is staggered and the other is close
					\begin{itemize}
						\item if both stagger it's fine
					\end{itemize}
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Repeat (can shift to [6] for safety)
				\item Shift once Multicast resolves
					\begin{itemize}
						\item if Cold Blood is over and they haven't used Dispelga, shift
					\end{itemize}
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Blitz-Blitz
				\item Repeat until Deprotect/Imperil
			\end{itemize}
		\item \second
			\begin{itemize}
				\item Repeat until dead and other Raktavija barriers
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Haste-Shell all
				\item Bravery-Vigilance Sazh
			\end{itemize}
		\item Repeat the same process as before and kill the second Raktavija
			\begin{itemize}
				\item Keep him interrupted post-stagger to prevent Dispelga
			\end{itemize}
	\end{itemize}
\end{battle}

Get on a chocobo and activate Mission 60 (stone circle).
Warp to Oerba ($\uparrow\uparrow$).
Run back to Taejin's and use the elevator.

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item \paradigmdeck{%
  				\paradigmline{Sazh}{Snow}{Vanille}}%
				{\paradigmline[4]{(\rav)}{\rav}{\sab}}%
				{\paradigmline{\com)}{(\com)}{(\com)}}%
				{\paradigmline{\com}{(\rav)}{\med}}%
				{\paradigmline{\com}{\sen}{\med}}%
				{\paradigmline{\syn}{\sen}{(\sab)}}%
				{\paradigmline{(\com)}{(\com)}{\med}}%
		\end{itemize}
	\equip
		\begin{itemize}
			\item Snow
				\begin{itemize}
					\item Shaman's Mark Lv.1
					\item Sorcerer's Mark Lv.1
					\item Sorcerer's Mark*
				\end{itemize}
			\item Vanille ($\rightarrow$)
				\begin{itemize}
					\item Witch's Bracelet* $\rightarrow$ Aurora Scarf Lv.1
					\item Witch's Bracelet* $\rightarrow$ Sprint Shoes Lv.1
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\first}{[1] Smart Bomb (\rav/\rav/\sab)}
\renewcommand{\second}{[2] Cerberus (\com/\com/\com)}
\renewcommand{\third}{[3] Thaumaturgy (\rav\rav\med)}
\renewcommand{\fifth}{[5] Premeditation (\syn/\sen/\sab)}
\renewcommand{\sixth}{[6] Tireless Charge (\com/\com/\med)}

Use a \textbf{Deceptisol} to dodge the Amphisbaena and for the fight.

\begin{battle}{Mission 60: Gelatitan x3 -- Pre-Empt}
	\begin{itemize}
		\item \first
			\begin{itemize}
				\item Quake
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Auto-Support
				\item Bravery-Enthunder Sazh
				\item Enthunder-Faith Snow ($\uparrow$)
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Blitz-Blitz
				\item Repeat
			\end{itemize}
		\item \second
			\begin{itemize}
				\item Repeat until victory
			\end{itemize}
	\end{itemize}
\end{battle}

Activate Mission 27.

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item \paradigmdeck{%
  				\paradigmline{Sazh}{Snow}{Vanille}}%
				{\paradigmline{\rav}{\rav}{(\rav)}}%
				{\paradigmline{\com}{\com}{\com}}%
				{\paradigmline{\rav}{\rav}{\med}}%
				{\paradigmline[4]{\com}{\sen}{\med}}%
				{\paradigmline{\syn}{\sen}{(\med)}}%
				{\paradigmline{\com}{\com}{(\med)}}%
		\end{itemize}
	\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Deneb Duellers*
					\item Diamond Bangle*
					\item Sorcerer's Mark Lv.1
					\item Tetradic Tiara Lv.1
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\first}{[1] Tri-Disaster (\rav/\rav/\rav)}
\renewcommand{\fifth}{[5] Protection (\syn/\sen/\med)}

Take the elevator to the ground floor (\textbf{skip the cutscene}).
\vfill

\begin{battle}{Mission 27: Mithridates}
	\begin{itemize}
		\item \fourth
			\begin{itemize}
				\item Blitz to cancel Miasma, then shift
			\end{itemize}
		\item \fifth
			\begin{itemize}
				\item Haste-Vigilance all
				\item Faith-Enfire all
			\end{itemize}
		\item \fourth
			\begin{itemize}
				\item Ruin x5
			\end{itemize}
		\item \first
			\begin{itemize}
				\item Fire-Aero-Fire-Aero-Fire
				\item Repeat, refresh with [3] until \stagger
				\item Cold Blood
			\end{itemize}
		\item \sixth
			\begin{itemize}
				\item Repeat, RAC Snow
			\end{itemize}
		\item \second
			\begin{itemize}
				\item Repeat until victory, maintain interruption
			\end{itemize}
	\end{itemize}
\end{battle}

Take the elevator back to the top and make your way to Oerba to activate Mission 64 (where Bart 2 was).
On the way back, Decept and kill the Seekers if no space to dodge.

\begin{battle}{Seeker x2 \& Varcolaci x2}
	\begin{itemize}
		\item \fourth
			\begin{itemize}
				\item Shift immediately
			\end{itemize}
		\item \second
			\begin{itemize}
				\item Ruin x5 until victory
			\end{itemize}
	\end{itemize}
\end{battle}

Warp to Paddraean Archaeopolis ($\downarrow$).

\begin{menu}
	\begin{itemize}
	\paradigm
		\begin{itemize}
			\item Battle Team
				\begin{itemize}
					\item Swap Sazh with Vanille (1 $\leftrightarrow$ 3)
				\end{itemize}
			\item \paradigmdeck{%
  				\paradigmline{Vanille}{Snow}{Sazh}}%
				{\paradigmline{\rav}{(\com)}{\rav}}%
				{\paradigmline{\com}{\com}{\com}}%
				{\paradigmline{(\sab)}{(\sen)}{\rav}}%
				{\paradigmline[4]{(\sab)}{\sen}{(\rav)}}%
				{\paradigmline{\med}{(\syn)}{\syn}}%
				{\paradigmline{(\sen)}{(\sen)}{(\sen)}}%
		\end{itemize}
	\equip
		\begin{itemize}
			\item Sazh
				\begin{itemize}
					\item Diamond Bangle* $\rightarrow$ Witch's Bracelet*
				\end{itemize}
			\item Snow ($\leftarrow$)
				\begin{itemize}
					\item Black Belt*
					\item General's Belt*
					\item Witch's Bracelet*
				\end{itemize}
			\item Vanille ($\leftarrow$)
				\begin{itemize}
					\item Aurora Scarf Lv.1 $\rightarrow$ Diamond Bangle*
					\item Sprint Shoes Lv.1 $\rightarrow$ Witch's Bracelet*
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{menu}

\renewcommand{\first}{[1] Relentless Assault (\rav/\com/\rav)}
\renewcommand{\second}{[2] Cerberus (\com/\com/\com)}
\renewcommand{\third}{[3] Matador (\sab/\sen/\rav)}
\renewcommand{\fourth}{[4] Matador (\sab/\sen/\rav)}
\renewcommand{\fifth}{[5] Recuperation (\med/\syn/\syn)}
\renewcommand{\sixth}{[6] Tortoise (\sen/\sen/\sen)}

Use \textbf{Fortisol}, \textbf{Aegisol} and \textbf{Ethersol} before the fight.
\vfill

\begin{battle}{Mission 64: Vercingetorix}
	\textit{\textbf{Phase 1}}
	\begin{itemize}
		\item \fourth
			\begin{itemize}
				\item Poison x5
				\item Summon
				\item Repeat until Verci's sixth attack
				\item X -- Gestalt
					\begin{itemize}
						\item Up+A to stall
						\item Let the last point run out
					\end{itemize}
			\end{itemize}
	\end{itemize}
	\textit{\textbf{Phase 2}}
	\begin{itemize}
		\item \first
			\begin{itemize}
				\item Elixir
				\item Auto-Chain
					\begin{itemize}
						\item Let Snow get close
					\end{itemize}
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Repeat
				\item Shift to the other Matador when Verci comes out of Aura for Challenge
				\item Repeat
				\item Summon
				\item Repeat until Verci's eighth attack
				\item X -- Gestalt
					\begin{itemize}
						\item Up+A to stall
						\item Let the last point run out
					\end{itemize}
			\end{itemize}
	\end{itemize}
	\textit{\textbf{Phase 3/4}}
	\begin{itemize}
		\item \textit{\textbf{Rebuff in 5 if needed}}
		\item \first
			\begin{itemize}
				\item Elixir
				\item Auto-Chain
					\begin{itemize}
						\item Let Snow get close
					\end{itemize}
			\end{itemize}
		\item \third
			\begin{itemize}
				\item Repeat
					\begin{itemize}
						\item \textit{If Snow didn't Challenge before Whicked Whirl, Summon to tank it}
						\item \textit{If Snow did Challenge before Whicked Whirl, shift to [6] to tank it}
						\item \textit{Renew if Vanille is significantly damaged}
					\end{itemize}
				\item Summon
				\item Repeat until Verci's eighth attack
				\item X -- Gestalt
					\begin{itemize}
						\item Up+A to stall
						\item Let the last point run out
					\end{itemize}
			\end{itemize}
	\end{itemize}
\end{battle}

Warp to the Base Camp ($\downarrow$), then back to Orphan's Cradle.
\vfill\null
\columnbreak
